EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-06-02 05_examples.tex
v1.1.2 updated 05_examples.tex added figures and script into figures. compiles independently as for arXiv.

\begin{figure}[t!]
    \includegraphics[width=0.5\linewidth]
        {edipack2_examples/edipack2triqs/G_iw.pdf}
    \includegraphics[width=0.5\linewidth]
        {edipack2_examples/edipack2triqs/A_w.pdf}
    \caption{\label{figEx3}%
        Imaginary part of the Matsubara Green's function $G_\alpha(i\omega_n)$ (left) and the
        corresponding orbital-resolved spectral function $A_\alpha(\omega) = -\Im{G_\alpha(\omega)} / \pi$ (right) computed for a
        three-orbital impurity model with an interaction of the Hubbard-Kanamori
        type (\ref{Hint}). This illustration is produced by the EDIpack2TRIQS
        example script presented in \secu{SecExamplesTRIQS}.
    }
\end{figure}

@@

A Python script implementing a calculation that makes use of EDIpack2TRIQS
generally begins with a few module imports.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=1, lastline=13]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}

One then proceeds to defining the system under consideration. In this case we
consider an impurity atom with three correlated orbitals and two bath states
per each impurity orbital, which corresponds to {\tt bath\_type=normal} in \NAME. This information must be encoded in the fundamental
set objects that are later used to construct the solver.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=15, lastline=26]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The next step is to define a TRIQS many-body operator expression that represents
the Hamiltonian to be diagonalized.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=28, lastline=67]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
Finally, one creates a solver object and performs the actual calculation by
calling its method {\tt solve()}. This is normally the most time- and
memory-consuming step.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=69, lastline=83]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The computation results are readily available as attributes of the solver
object. The following code snippet shows how to access measured expectation
values of the static observables, and how to employ the plotting framework of
TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
functions (\figu{figEx3}).
\lstinputlisting[style=mypython,
                 mathescape=false,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=85, lastline=113]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}

>>>>

\begin{figure}[t!]
    \includegraphics[width=0.5\linewidth]
        {figures/G_iw.pdf}
    \includegraphics[width=0.5\linewidth]
        {figures/A_w.pdf}
    \caption{\label{figEx3}%
        Imaginary part of the Matsubara Green's function $G_\alpha(i\omega_n)$ (left) and the
        corresponding orbital-resolved spectral function $A_\alpha(\omega) = -\Im{G_\alpha(\omega)} / \pi$ (right) computed for a
        three-orbital impurity model with an interaction of the Hubbard-Kanamori
        type (\ref{Hint}). This illustration is produced by the EDIpack2TRIQS
        example script presented in \secu{SecExamplesTRIQS}.
    }
\end{figure}

@@

A Python script implementing a calculation that makes use of EDIpack2TRIQS
generally begins with a few module imports.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=1, lastline=13]
{figures/hubbard_kanamori.py}

One then proceeds to defining the system under consideration. In this case we
consider an impurity atom with three correlated orbitals and two bath states
per each impurity orbital, which corresponds to {\tt bath\_type=normal} in \NAME. This information must be encoded in the fundamental
set objects that are later used to construct the solver.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=15, lastline=26]
{figures/hubbard_kanamori.py}
The next step is to define a TRIQS many-body operator expression that represents
the Hamiltonian to be diagonalized.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=28, lastline=67]
{figures/hubbard_kanamori.py}
Finally, one creates a solver object and performs the actual calculation by
calling its method {\tt solve()}. This is normally the most time- and
memory-consuming step.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=69, lastline=83]
{figures/hubbard_kanamori.py}
The computation results are readily available as attributes of the solver
object. The following code snippet shows how to access measured expectation
values of the static observables, and how to employ the plotting framework of
TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
functions (\figu{figEx3}).
\lstinputlisting[style=mypython,
                 mathescape=false,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=85, lastline=113]
{figures/hubbard_kanamori.py}
